\documentclass[edeposit,fullpage]{uiucthesis2018}

\usepackage[acronym,toc]{glossaries}
\include{acros}

\usepackage{xspace}
\usepackage{graphics}

\usepackage{placeins}
\usepackage{booktabs} % nice rules (thick lines) for tables
\usepackage{microtype} % improves typography for PDF

\usepackage[hyphens]{url}
\usepackage{hyperref}
\usepackage{subfig}
\usepackage{hhline}
\usepackage{amsmath}
\usepackage{color}
\usepackage{multirow}
\usepackage{siunitx}
\sisetup{
    input-decimal-markers = .,input-ignore = {,},table-number-alignment = right,
    group-four-digits = true
}
\usepackage{fourier}
\usepackage{booktabs}
\newcommand\tab[1][1cm]{\hspace*{#1}}

\usepackage{threeparttable, tablefootnote}

%tikzpicture fit to page width
\usepackage{environ}
\makeatletter
\newsavebox{\measure@tikzpicture}
\NewEnviron{scaletikzpicturetowidth}[1]{%
  \def\tikz@width{#1}%
  \def\tikzscale{1}\begin{lrbox}{\measure@tikzpicture}%
  \BODY
  \end{lrbox}
  \pgfmathparse{#1/\wd\measure@tikzpicture}%
  \edef\tikzscale{\pgfmathresult}%
  \BODY
}

\usepackage{tabularx}
\newcolumntype{b}{>{\hsize=1.0\hsize}X}
\newcolumntype{q}{>{\hsize=0.5\hsize}X}
\newcolumntype{R}{>{\raggedleft\arraybackslash\hsize=0.5\hsize}X}
\newcolumntype{z}{>{\hsize=0.75\hsize}X}
\newcolumntype{s}{>{\hsize=.5\hsize}X}
\newcolumntype{m}{>{\hsize=.75\hsize}X}

\usepackage{cleveref}
\usepackage{datatool}
\usepackage[numbers]{natbib}
\usepackage{notoccite}

\usepackage{tikz}
\usetikzlibrary{positioning, arrows, decorations, shapes}

\usetikzlibrary{shapes.geometric,arrows}
\tikzstyle{process} = [rectangle, rounded corners, minimum width=2.5cm, minimum height=1cm,text centered, draw=black, fill=blue!30]

\tikzstyle{object} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=green!30]
\tikzstyle{objectr} = [ellipse, rounded corners, minimum width=3cm, minimum height=1cm,text centered, draw=black, fill=red!30]

\tikzstyle{empty} =  [rectangle, rounded corners, minimum width=2.5cm, minimum height=0.7cm,text centered, draw=black, fill=white!30]
\tikzstyle{arrow} = [thick,->,>=stealth]

%% Added by me
\usepackage{tabularx}
\usepackage{float}
\usepackage{enumitem}
% \usepackage{subcaption}
% \usepackage[titletoc]{appendix}
\usepackage{appendix}

%\title{Moltres application to prismatic gas-cooled reactors}
%\title{Moltres application to prismatic gas-cooled reactors and high-temperature hydrogen production}
\title{Multi-physics and technical analysis of high-temperature gas-cooled reactors for hydrogen production}
\author{Roberto E. Fairhurst Agosta}
\department{Nuclear, Plasma, and Radiological Engineering}
\concentration{Computational Science and Engineering}
% \schools{B.S., University of Illinois - Urbana Champaign, 2017}
\msthesis
\advisor{Kathryn D. Huff}
\degreeyear{2020}
\committee{Assistant Professor Kathryn D. Huff, Advisor \\ Associate Professor and Associate Head for Undergraduate Programs, Tomasz Kozlowski}

\begin{document}
\maketitle

\frontmatter
%% Create an abstract that can also be used for the ProQuest abstract.
%% Note that ProQuest truncates their abstracts at 350 words.
\begin{abstract}

% climate change and HTGRs role
The future energy needs require the development of clean energy sources to ease the increasing environmental concerns.
High-Temperature Gas-cooled Reactors have several desirable features that make them ideal candidates for the near-future large-scale deployment.
Some of these features are a high temperature and high thermal cycle efficiency, which enable a wide range of process heat applications, such as hydrogen production.
Implementing hydrogen economies can decarbonize the transport and power sectors, offering an alternative to ease climate change.

% what did this work do
This work uses Moltres as the primary simulation tool.
Although Moltres original development targeted Molten Salt Reactors, this work studies Moltres applicability to multi-physics simulations of prismatic High-Temperature Gas-cooled Reactors.
Multi-physics simulations are necessary for assessing reactor safety characteristics.
Ensuring Moltres' multi-physics modeling capabilities requires assessing the independent modeling capabilities of the different involved physical phenomena.
Therefore, this thesis breaks down the analysis into three parts: stand-alone neutronics, stand-alone thermal-fluids, and coupled neutronics/thermal-fluids.

% results: ch4
Regarding stand-alone neutronics, several analyses compare the results calculated by Moltres and Serpent on a model of the MHTGR-350.
The first analysis studies the energy group structure effects on the simulation of a fuel column.
The results of the study suggest using a 15-energy group structure for attaining a desirable accuracy.
The following analysis focuses on the full-core problem and compares different aspects of the simulations, concluding that Moltres obtains reasonably accurate results.
The final study on stand-alone neutronics describes Moltres results of Phase I Exercise 1 of the OECD/NEA MHTGR-350 Benchmark.
The benchmark exercise proved to be a modeling challenge, requiring the implementation of several approximations.
For the most part, this thesis demonstrates Moltres' capability to simulate stand-alone neutronics of prismatic High-Temperature Gas-cooled Reactors.

% results: ch5
Regarding stand-alone thermal-fluids, several studies compare Moltres results to previously published results.
These studies focus on local models such as the unit cell and the fuel column problems, for which Moltres results differ by less than 2\% from the published results.
Further studies analyze the possibility of extending the thermal-fluids model implemented in the previous problems to a full-core simulation, finding a high memory requirement imposed by the simulations.
The full-core simulations focus on Phase I Exercise 2 of the benchmark, for which the implementation of a two-level approach in Moltres was necessary.
The study's results were within an 11.3\% difference to the published results, concluding that further analysis is required.

% results: ch5-coupled
Regarding coupled neutronics/thermal-fluids, the analysis describes Phase I Exercise 3 of the benchmark.
The exercise uses a simplified model that helps visualize some of the essential aspects of multi-physics simulations in Moltres.
This exercise finds some flaws in Moltres' model and sets a basis for future work.

% results: ch 6
This thesis aligns with the University of Illinois' goals to reduce carbon emissions from its campus's electricity generation and transportation sectors.
This work focuses on two main analysis by introducing a nuclear reactor coupled to a hydrogen plant as a solution.
The first analysis evaluates the conversion of the university fleet along with the mass transit transport system in Urbana-Champaign to Fuel Cell Electric Vehicles.
The second analysis investigates the duck curve phenomenon in the university's grid and introduces a mitigation strategy that may reduce the reliance on dispatchable sources.
These studies emphasize how nuclear energy and hydrogen production can potentially mitigate climate change.

\end{abstract}

\begin{dedication}
A mi familia, for their unconditional support.
\end{dedication}

\chapter*{Acknowledgments}
\input{acks}

%% The thesis format requires the Table of Contents to come
%% before any other major sections, all of these sections after
%% the Table of Contents must be listed therein (i.e., use \chapter,
%% not \chapter*).  Common sections to have between the Table of
%% Contents and the main text are:
%%
%% List of Tables
%% List of Figures
%% List Symbols and/or Abbreviations
%% etc.

\tableofcontents
\listoftables
\listoffigures

%% Create a List of Abbreviations. The left column
%% is 1 inch wide and left-justified
%\chapter{List of Abbreviations}
%\printglossaries
%% Create a List of Symbols. The left column
%% is 0.7 inch wide and centered

\pagebreak
\mainmatter

% different chapters
\chapter{Introduction}
\input{introduction}

\chapter{Literature Review}
\input{litreview}

\chapter{Methodology}
\input{methodology}

\chapter{Neutronics}
\input{neutronics}

\chapter{Thermal-fluids}
\input{thermalfluids}

\chapter{Hydrogen Production}
\input{hydrogen}

\chapter{Conclusions}
\input{conclusions}

\begin{appendices}
	\chapter{Equations}
	\input{appendixA}
	\chapter{Group Constants Handling}
	\input{appendixB}
	\chapter{Analytical Solutions}
	\input{appendixC}
\end{appendices}

% \chapter*{Appendix A}
% \setcounter{chapter}{8}
% \setcounter{section}{0}
% \setcounter{equation}{0}
% \input{appendixA}

% \chapter*{Appendix B}
% \setcounter{chapter}{9}
% \setcounter{section}{0}
% \setcounter{equation}{0}
% \input{appendixB}

% \chapter*{Appendix C}
% \setcounter{chapter}{10}
% \setcounter{section}{0}
% \setcounter{equation}{0}
% \input{appendixC}

\backmatter

% \bibliographystyle{apalike}
\bibliographystyle{ieeetr}
\bibliography{bibliography}

\end{document}
\endinput
%%
%% End of file
